%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Career Highlights}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Geophysics Research Scientist} % Job title
    {European Space Agency} % Organisation
    {Noordwijk, Netherlands} % Location
    {October 2024 - October 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Detecting gravity anomalies in asteroids, by reconstructing their density distribution. I’m expected to spend at least a year at \href{https://maps.app.goo.gl/VygAGAxH79ZLLgZW7}{\color{darkblue}{ESTEC}} (European Space Research and Technology Centre) in the \href{https://www.esa.int/gsp/ACT/}{\color{darkblue}{ACT}} (Advanced Concepts Team) group, developing theory and methods to use artificial intelligence for solving inverse gravity problems.  
        }
        \item {This will be completed alongside my PhD, why by my supervisor at ESA will be \href{https://www.esa.int/gsp/ACT/team/dario_izzo/}{\color{darkblue}{Dr Dario Izzo}}.}
      \end{cvitems}
    }

  \cventry
    {Food and Beverage Assistant} % Job title
    {Ensana Hotels, Buxton Crescent Hotel} % Organisation
    {Buxton, UK} % Location
    {August 2023 - December 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working full time, in the hospitality industry.}
        \item {Frequently working all positions in the hotel restaurant, often being solely responsible for its operation.}
        \item{Often was the sole bartender, during large functions and at the companies sister hotel (Old Hall Hotel - Buxton, UK).}
      \end{cvitems}
    }
    
  \cventry
    {Farm Hand and Labourer} % Job title
    {TP. Morten and Sons Dairy Farm} % Organisation
    {Nr Buxton, UK} % Location
    {January 2014 - July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {General farm labourer, driver and machinery operator.}
        \item {Combination of full time and part time work as a general manual labourer on a family- owned Dairy Farm.}
        \item{Responsibility was instilled on me from a young age, varying in roles from things such as the use, and maintenance of valuable and hazardous pieces of machinery} 
        \item{Working with large animals in a variety of environments and locations, often in confined spaces, where maintaining a high degree of personal safety was paramount.}
      \end{cvitems}
    }
\end{cventries}
