%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%As the formatting was messy and I didn't want the title "Voluntering" to be on the prior page
%\newpage{}

\cvsection{Volunteering}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

  \cventry
    {University of Liverpool, Herdman Student Society} % Organisation
    {Society Treasurer} % Project
    {Liverpool, UK} % Location
    {September 2022 - September 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Peer elected as apart of an academic society for anybody interested in the Earth Sciences, ranging from Undergraduates to Professors.}
        \item {Directly involved with the organising and running of a weekly extra-curricular lecture series where faculty can attend and learn about topics related to the earth sciences with related talks from academics, or related industries. For instance, talks have been led by \href{https://tektonik.co.uk/}{\color{darkblue}{Tektonik Consulting Ltd}}, and \href{https://rskgroup.com/}{\color{darkblue}{RSK}}.
        }
        \item {The society also holds a yearly Symposium, which is a careers and networking event all students and staff can attend.}
      \end{cvitems}
    }

  \cventry
    {Dig Deep  (Africa)} % Organisation
    {Volunteer Fundraiser } % Project
    {Bomet County, Kenya} % Location
    {May 2021 - August 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {I have a passion for hiking, this summer having worked extensively with a UK based charity \href{https://www.digdeep.org.uk/}{\color{darkblue}{(Dig Deep)}} - together with a group from Liverpool, we summited Mt Kilimanjaro, Tanzania (Informally – we were the “Kilimanscousers”).}
        \item {As a group we raised a total of £34,293 for charity.}
        \item {The money has gone towards improving clean water access, creating safe toilets, and good hygiene for some of Kenya’s poorest residents.}
      \end{cvitems}
    }

  \cventry
    {Altrad Belle (Belle Engineering (Sheen) Ltd)} % Organisation
    {A weeks work experience at a light engineering company} % Project
    {Sheen, UK} % Location
    {May 2019 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item{Worked as a part of the Research and Development Department.}
        \item {I was involved in the discovery of assembly problems with Plate Compactors – incorrect gearbox assembly was leading to the construction of destructive harmonics, causing no directional motion.}
        \item {I learnt how to work practically with my hands and using other pieces of machinery / tools in a safe and controlled manner.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
